Programming Assignment 2

### 2015-04-02 paper.tex
Update paper.tex
Merrggiinnnngggggggg

\subsubsection{Classifications}
The classifications used by BAM were encoded as orthogoal vectors of length 6.
Each class 'supersection' had a total of 3 classes. The animal supersection
includes Dogs, Elephants, and Giraffes. The Plane supersection includes Biplanes,
Jets, and Airbuses. Finally the Marine supersection includes Ships, Submarines,
and Whales. Each supersection is treated separately. The encodings for Animals
are used again in Planes and Marines. This was to make the classification
encodings as simple yet distant as possible.
\subsection{Performance}
The Bidirectional Associative Memory implementation performed rather poorly.
Most of the associations were directed towards a specific centroid, resulting
in at least 1 'class' performing extremely well. The results of our
experiment are as follows.
Animal Results:
    Dog:
        7 Correctly Classified
        3 Incorrectly Classified
    Elephant:
        1 Correctly Classified
        9 Incorrectly Classified
    Giraffe:
        0 Correctly Classified
        9 Correctly Classifed
Plane Results:
    Biplane:
        0 Correctly Classified
        10 Incorrectly Classified
    Jet Results:
        5 Correctly Classified
        5 Incorrectly Classified
    Airbus Results:
        0 Correctly Classified
        7 Incorrectly Classified
Marine Results:
    Ships:
        0 Correctly Classified
        5 Incorrectly Classified
    Submarine Results:
        8 Correctly Classified
        0 Incorrectly Classified
    Whale Results:
        3 Correctly Classified
        7 Incorrectly Classified

It seems that the BAM implementation attempted to classify nearly all animals
as dogs. For planes the network had more diverse attempts to classify each
object, although incorrectly. The marine results showed the most diverse and
correct classifications. Although it does seem that BAM attempted to describe
everything as either a submarine or a whale.

@@

\subsection{Comments}
BAM performed rather poorly. It appeared that BAM favored a single class when
attempting to classify. However I believe this is a result of our encoding 
scheme. If we had made our own outlines our network could have performed 
better. Larger sizes could also give some accuracy in exchange for computational
power.

@@

\section{Member Assignments}
All members were involved in some manner in all major area of the project. These
major areas include the paper writup, the presentation creation, and the 
programming. The specific assignements per group member are given below, but no
single member handled an entire area of development.
\subsection{Jonathan Brandt}
\subsubsection{Programming}
Jonathan's programming work was divided between implementation of the 
Hamming/Max network and the creation of centroids for the networks based on a
large number of sample inputs. He was completely responsible for creating the Hamming layer of the Hamming/MAX network, and worked in conjunction with the rest of the team when creating the centroids.

\subsubsection{Project Report}
Jonathan was tasked with the Hamming/Max section. He also was in charge of reporting on the Overview section.

\subsubsection{Project Presentation}
Jonathan updated the project with accurate testing results

>>>>

\subsubsection{Classifications}
The classifications used by BAM were encoded as orthogoal vectors of length 6. 
Each class 'supersection' had a total of 3 classes. The animal supersection 
includes Dogs, Elephants, and Giraffes. The Plane supersection includes Biplanes, 
Jets, and Airbuses. Finally the Marine supersection includes Ships, Submarines, 
and Whales. Each supersection is treated separately. The encodings for Animals 
are used again in Planes and Marines. This was to make the classification 
encodings as simple yet distant as possible.

\subsection{Performance}
The Bidirectional Associative Memory implementation performed rather poorly. 
Most of the associations were directed towards a specific centroid, resulting 
in at least 1 'class' performing extremely well. The results of our 
experiment are as follows.

\begin{itemize}
    \item Animals
        \begin{itemize}
            \item Dog Results:
                \begin{itemize}
                    \item Classified as Dog:........7
                    \item Classified as Elephant:...0
                    \item Classified as Giraffe:....2
                    \item Classified as Unknown:....1
                \end{itemize}
            \item Elephant Results:
                \begin{itemize}
                    \item Classified as Dog:........0
                    \item Classified as Elephant:...1
                    \item Classified as Giraffe:....1
                    \item Classified as Unknown.....8
                \end{itemize}
            \item Giraffe Results:
                \begin{itemize}
                    \item Classified as Dog:........0
                    \item Classified as Elephant:...0
                    \item Classified as Giraffe:....9
                    \item Classified as Unknown:....0
                \end{itemize}
        \end{itemize}
    \item Planes
        \begin{itemize}
            \item Biplane Results:
                \begin{itemize}
                    \item Classified as Biplane:....0
                    \item Classified as Jet:........3
                    \item Classified as Airbus:.....0
                    \item Classified as Unknown:....7
                \end{itemize}
            \item Jet Results:
                \begin{itemize}
                    \item Classified as Biplane:....0
                    \item Classified as Jet:........5
                    \item Classified as Airbus:.....0
                    \item Classified as Unknown:....5
                \end{itemize}
            \item Airbus Results:
                \begin{itemize}
                    \item Classified as Biplane:....0
                    \item Classified as Jet:........4
                    \item Classified as Airbus:.....0
                    \item Classified as Unknown:....3
                \end{itemize}
        \end{itemize}
    \item Marines
        \begin{itemize}
            \item Ship Results:
                \begin{itemize}
                    \item Classified as Ship:.......0
                    \item Classified as Submarine:..0
                    \item Classified as Whale:......0
                    \item Classified as Unknown:....5
                \end{itemize}
            \item Submarine Results:
                \begin{itemize}
                    \item Classified as Ship:.......0
                    \item Classified as Submarine:..8
                    \item Classified as Whale:......0
                    \item Classified as Unknown:....0
                \end{itemize}
            \item Whale Results:
                \begin{itemize}
                    \item Classified as Ship:.......0
                    \item Classified as Submarine:..5
                    \item Classified as Whale:......3
                    \item Classified as Unknown:....2
                \end{itemize}
        \end{itemize}
\end{itemize}

While often the BAM misclassified objects, most of the time it told us that
it could not classify it. Our BAM implementation could not classify Elephants, 
Biplanes, and Ships but it could tell us that of the inputs used, it could not
classify them. Otherwise the network performed extremely well with objects
such as dogs and submarines.

Of the occasions that the BAM network misclassified, such as the airbus, this is 
likely due to a poorly defined centroid. If we had improved our encoding perhaps 
we could have gotten some better results.

@@

\subsection{Comments}
BAM performed rather poorly overall. It appeared that BAM favored a single class when 
attempting to classify. However I believe this is a result of our encoding 
scheme. If we had made our own outlines our network could have performed 
better. Larger sizes could also give some accuracy in exchange for computational 
power.

@@

\section{Member Assignments}
All members were involved in some manner in all major area of the project. These
major areas include the paper writup, the presentation creation, and the 
programming. The specific assignements per group member are given below, but no
single member handled an entire area of development.
\subsection{Jonathan Brandt}
\subsubsection{Programming}
Jonathan's programming work was divided between implementation of the 
Hamming/Max network and the creation of centroids for the networks based on a
large number of sample inputs. He was completely responsible for creating the Hamming layer of the Hamming/MAX network, and worked in conjunction with the rest of the team when creating the centroids. He was responsible for testing the HAM and LVQ networks in whole and gathering the results.

\subsubsection{Project Report}
Jonathan was tasked with the Hamming/Max section. He also was in charge of reporting on the LVQ section and filling in result data.

\subsubsection{Project Presentation}
Jonathan updated the project with accurate testing results.
